### 2016-10-31 Manuscript/SW_early_life_telomeres.Rmd
Edits
Home edits

dd14 <- subset(dd,DeathYear<2015)
dd14$RowID <- c(1:nrow(dd14))

summary(glmer(SurvivedNext~RTL * LogAge + Tarsus + Sex + (1|BirdID)+(1|LayYear),data=dd14,family = 'binomial'))

ggplot(dd14,aes(x = Agemonths, col = factor(SurvivedNext),y = RTL))+
geom_smooth(method = 'lm',formula = y~log(x))

>>>>

m1 <- lmer(RTL~Agemonths+(1|BirdID) + (1|LayYear),data=dd)
m2 <- lmer(RTL~LogAge+(1|BirdID) + (1|LayYear),data=dd)
m3 <- lmer(RTL~factor(Agemonths)+(1|BirdID) + (1|LayYear),data=dd)

dd14 <- subset(dd,DeathYear<2015)

summary(glmer(SurvivedNext~RTL*LogAge + (1|LayYear) + (1|BirdID),data=dd14,family = 'binomial'))

?coxph
summary(coxph(Surv(RemainingLife,Died)~RTL*LogAge,data=dd14))

### 2016-10-31 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
Home edits

Fig1D <- ggplot(temp,aes(y = DeltaRTL,x = TimeDiff))+
    geom_point(col = 'grey')+
  theme_classic()+ 
  xlab ('Follow up time (years)')+
  ylab(expression(Delta*'RTL'))+
  ylim(c(-2,2))+
    theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_blank(),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
    geom_abline(slope = 0,intercept = 0,lty = 2)+
  annotate('text',x = 0,y = 2,label = 'D')

>>>>

temp <- dd3
dd3
props <- tapply(dd3$DeltaRTLF,dd3$TimeDiff,mean)
propn <- tapply(dd3$DeltaRTLF,dd3$TimeDiff,length)
temp <- data.frame(props,propn,TimeDiff = as.numeric(names(props))/12) %>%
  subset(propn > 10)

Fig1D <- ggplot(temp,aes(y = props,x = TimeDiff))+
    geom_point(col = 'grey')+
  theme_classic()+ 
  xlab ('Follow up time (years)')+
  ylab('Proportion gainers')+
    theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_blank(),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'))
